Examining background gene lists in clusterProfiler - scRNA-seq example

### 2023-08-30 analysis/example_proteomics.Rmd
updates

barplot(c(topdn2,topup2),
  horiz=TRUE,las=1,cex.names=0.65,col=cols,
  main="top DE KEGGs",
  xlab="ES",
  cex.main=0.9)

mtext("ORA test")

@@

barplot(c(topdn2,topup2),
  horiz=TRUE,las=1,cex.names=0.65,col=cols,
  main="top DE KEGGs",
  xlab="ES",
  cex.main=0.9)

mtext("ORA fix test")

@@

@@

barplot(c(topdn2,topup2),
  horiz=TRUE,las=1,cex.names=0.65,col=cols,
  main="top DE Reactomes",
  xlab="ES",
  cex.main=0.9)

mtext("ORA test")

@@

barplot(c(topdn2,topup2),
  horiz=TRUE,las=1,cex.names=0.65,col=cols,
  main="top DE Reactomes",
  xlab="ES",
  cex.main=0.9)

mtext("ORA fix test")

@@

>>>>

top <- c(topdn2,topup2)

if ( length(top) > 1 ) {
  barplot(c(top),
    horiz=TRUE,las=1,cex.names=0.65,col=cols,
    main="top DE KEGGs",
    xlab="ES",
    cex.main=0.9)
  mtext("ORA test")
}

@@

top <- c(topdn2,topup2)

if ( length(top) > 1 ) {
  barplot(c(top),
    horiz=TRUE,las=1,cex.names=0.65,col=cols,
    main="top DE KEGGs",
    xlab="ES",
    cex.main=0.9)
  mtext("ORA fix")
}

@@

png("prot_kegg_euler.png")
plot(euler(v3),quantities = list(cex = 2), labels = list(cex = 2),main="up- and down-regulated KEGG pathways")
dev.off()

@@

top <- c(topdn2,topup2)

if ( length(top) > 1 ) {
  barplot(c(top),
    horiz=TRUE,las=1,cex.names=0.65,col=cols,
    main="top DE Reactomes",
    xlab="ES",
    cex.main=0.9)
  mtext("ORA test")
}

@@

top <- c(topdn2,topup2)

if ( length(top) > 1 ) {
  barplot(c(top),
    horiz=TRUE,las=1,cex.names=0.65,col=cols,
    main="top DE Reactomes",
    xlab="ES",
    cex.main=0.9)
  mtext("ORA fix")
}

@@

png("prot_reactome_euler.png")
plot(euler(v3),quantities = list(cex = 2), labels = list(cex = 2),main="up- and down-regulated Reactomes")
dev.off()

### 2023-08-30 analysis/example_rnaseq.Rmd
update
updates

writeLines(text=defup,con="aza_up.txt")
writeLines(text=defdn,con="aza_dn.txt")
writeLines(text=bg,con="aza_bg.txt")

@@

@@

barplot(c(topdn2,topup2),
  horiz=TRUE,las=1,cex.names=0.65,col=cols,
  main="top DE Reactomes",
  xlab="ES",
  cex.main=0.9)

mtext("ORA fix test")

@@

>>>>

writeLines(text=unique(defup),con="aza_up.txt")
writeLines(text=unique(defdn),con="aza_dn.txt")
writeLines(text=unique(bg),con="aza_bg.txt")

@@

png("rna_kegg_euler")
plot(euler(v3),quantities = list(cex = 2), labels = list(cex = 2),main="up- and down-regulated KEGG pathways")
dev.off()

@@

top <- c(topdn2,topup2)

if ( length(top) > 1 ) {
  barplot(c(top),
    horiz=TRUE,las=1,cex.names=0.65,col=cols,
    main="top DE Reactomes",
    xlab="ES",
    cex.main=0.9)
  mtext("ORA fix")
}
```

@@

png("rna_reactome_euler")
plot(euler(v3),quantities = list(cex = 2), labels = list(cex = 2),main="up- and down-regulated Reactomes")
dev.off()

### 2023-08-30 analysis/example_scrnaseq.Rmd
addition
updates

@@

@@

@@

@@

@@

ora <- union(ora_ups,ora_dns)

orafix <- union(orafix_ups,orafix_dns)

>>>>

if ( nrow(ora_res > 1 ) ) {

@@

}

@@

png("scrna_kegg_euler.png")
plot(euler(v3),quantities = list(cex = 2), labels = list(cex = 2),main="up- and down-regulated KEGG pathways")
dev.off()

@@

orasets <- c(up_sets,dn_sets)
orafixsets <- c(fixup_sets,fixdn_sets)

jaccard(orasets,orafixsets)

@@

png("scrna_reactome_euler.png")
plot(euler(v3),quantities = list(cex = 2), labels = list(cex = 2),main="up- and down-regulated Reactomes")
dev.off()

@@
